Another paper with lots of text and fancy pictures

### 2023-09-28 paper.tex
Fix some stuff

@@

\section{Theoretical background}
Let $A_1, A_2, \dots, A_n$ be pairwise disjoint subsets of a set
$A \subset \mathbb{R}^n$. We introduce a family of indicator functions
$I_n(x) : A \rightarrow \{0,1\}$ defined as:
\begin{equation}
  I_n(x) = \left\{
  \begin{array}{ll}
    1 & \quad x \in A \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}

Now we can define the three-point correlation function $S_3: A^2 \rightarrow [0, 1]$:
\begin{equation}
  S_3^n(x_1, x_2) = \langle I_n(x) I_n(x + x_1) I_n(x + x_2) \rangle
\end{equation}
It can be understood as the probability that all three vertices of a triangle
$(0, x_1, x_2)$ will appear in the subset $A_n$ when it is randomly thrown in
$A$. When $A$ represent isotropic medium, $x_1$ and $x_2$ can be replaced with
three numbers $r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$ to get a
function $S_3: [0, \infty)^3 \rightarrow [0, 1]$.

@@

\section{Verification}
To verify correctness of computation of $S_3$ and $C_3$ functions we use the
following simple relations:
\begin{align}
  & S_3^n (x, 0) = S_3^n (0, x) = S_2^n(x) \\
  & C_3^n (x, 0) = C_3^n (0, x) = C_2^n(x) \\
  & \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} S_3^n (x_1, x_2) =
  \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} C_3^n (x_1, x_2) = \phi_n^3
\end{align}
Here $\phi_n$ is a fraction of phase $n$ in $A$.

@@

\section{Results}
In this section we compute correlation functions along the plane $XY$ for some
real samples, namely one three-dimensional XCT and one two-dimensional SEM
sample. Table \ref{tab:summary} contains information about these samples. Note
that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
samples are on \cref{fig:samples}. On the plots of correlation functions we
provide a family of curves with the first argument of the correlation function
being fixed.

>>>>

\definecolor{light-gray}{gray}{0.95}
\newcommand{\code}[1]{\colorbox{light-gray}{\texttt{#1}}}

@@

\section{Theoretical background}
Let $A_1, A_2, \dots, A_n$ be pairwise disjoint subsets of a set
$A \subset \mathbb{R}^n$. We introduce a family of indicator functions
$I_n(x) : A \rightarrow \{0,1\}$ defined as:
\begin{equation}
  I_n(x) = \left\{
  \begin{array}{ll}
    1 & \quad x \in A_n \\
    0 & \quad \text{otherwise}
  \end{array}
  \right.
\end{equation}

Now we can define the three-point correlation function
$S_3: \mathbb{R}^2 \rightarrow [0, 1]$:
\begin{equation}
  S_3^n(x_1, x_2) = \langle I_n(x) I_n(x + x_1) I_n(x + x_2) \rangle
\end{equation}
where $\langle \dots \rangle$ means average over all points in $A$. It can be
understood as the probability that all three vertices of a triangle
$(0, x_1, x_2)$ will appear in the subset $A_n$ when the triangle is randomly
thrown in $A$. When $A$ represent isotropic medium, $x_1$ and $x_2$ can be
replaced with three numbers $r_1 = |x_1|$, $r_2 = |x_2|$ and $r_3 = |x_2 - x_1|$
to get a function of three scalar arguments.

@@

\section{Verification}
To verify correctness of computation of $S_3$ and $C_3$ functions we use the
following simple relations:
\begin{align}
  S_3^n (x, 0) = S_3^n (0, x) &= S_2^n(x) \\
  C_3^n (x, 0) = C_3^n (0, x) &= C_2^n(x) \\
  \lim_{\substack{x_1 \to \infty \\ x_2 \to \infty}} S_3^n (x_1, x_2) &= \phi_n^3
\end{align}
Here $\phi_n$ is a fraction of phase $n$ in $A$.

@@

\section{Results}
In this section we compute correlation functions along the plane $XY$ for some
real samples, namely one three-dimensional XCT and one two-dimensional SEM
sample. Table \ref{tab:summary} contains information about these samples. Note
that the criterion $C_{0.5} > 0.97$ holds for both of the samples. Images of the
samples are on \cref{fig:samples}. On plots of correlation functions we provide
a family of curves with the first argument of the correlation function being
fixed.
